Draft TLF generator

### 2023-04-28 posts/manipulate/draft_tlf_generator.qmd
Update draft_tlf_generator.qmd

Please find the code of this section in <font color="blue"> [add_model_name](https://posit.cloud/content/5870060) </font>

@@

      invisible(self)
    },
    remove = function(keys) {
      i = wf(!self$has(keys))
      rm(list = keys, envir = self$items)
      invisible(self)
    }
  )
)
```
#### Used functions

>>>>

Please find the code of this section in <font color="blue"> https://posit.cloud/content/5870060 </font>

@@

      invisible(self)
    },
    remove = function(outputs) {
      #check the outputs if exsit firstly
      rm(list = outputs, envir = self$tlfs)
      invisible(self)
    }
  )
)
```
#### Used functions
